Run models

### 2017-01-30 Code/3_validation/run-models.Rmd
models running

```{r load_libraries}
library(Rcpp)
library(dplyr)
library(purrr)
library(ggplot2)
library(stringr)
library(rjags)
library(R2jags) 
library(devtools)
library(jagstools)
library(reshape2)
library(parallel)
library(gtools)
library(bayesboot)
library(coda)
library(grid)
library(gridExtra)
```

@@

system.time(
  for(sex_i in c("Male", "Female")){
    for(state_i in c("Alabama", "Arizona", "Arkansas", "California")) {
      assign(paste0("r.White.", state_i, sex_i), run_analysis(dataset = dat.clean, state1 = state_i, sex1 = sex_i, race1 = "White"))
      assign(paste0("r.Black.", state_i, sex_i), run_analysis(dataset = dat.clean, state1 = state_i, sex1 = sex_i, race1 = "Black"))  
    }
  }
)

r.White <- rbind(r.White.Alabama.Male, r.White.Arizona.Male, r.White.Arkansas.Male, r.White.California.Male,
                 r.White.Alabama.Female, r.White.Arizona.Female, r.White.Arkansas.Female, r.White.California.Female)
r.White$race <- "White"

r.Black <- rbind(r.Black.Alabama.Male, r.Black.Arizona.Male, r.Black.Arkansas.Male, r.Black.California.Male,
                 r.Black.Alabama.Female, r.Black.Arizona.Female, r.Black.Arkansas.Female, r.Black.California.Female)
r.Black$race <- "Black"
```

@@

r.All$smoothed_deaths <- r.All$smoothed_rate*r.All$population

system.time(r.All <- r.All %>% group_by(post.samp, state, race.sex, year.n, age_minbin) %>%
                           arrange(post.samp, state, race.sex, year.n, age_minbin) %>%
                           mutate(total_smoothed_deaths = sum(smoothed_deaths),
                                  cod_prop_smoothed_deaths = smoothed_deaths/total_smoothed_deaths))
```

```{r run_calculations}
#run time ~40 mins -- expect 5.5 hours
#run the life table and decomposition calculations for each of the 1000 posterior samples

@@

```{r}
# load('~/SH_HA_data.Rdata')
# SH_sub <- dtotal %>% filter(state == "Alabama", sex == "Male", race == "Black", year == 1990)
# 
# SH_sub %>% select(age, age_minbin, deaths, population)
```

>>>>

```{r load_libraries}
library(Rcpp)
library(dplyr)
library(purrr)
library(ggplot2)
library(stringr)
library(rjags)
library(R2jags) 
library(devtools)
library(jagstools)
library(reshape2)
library(parallel)
library(gtools)
library(bayesboot)
library(coda)
library(grid)
library(gridExtra)
library(parallel)
```

@@

list_set2 <- list("Colorado", "Connecticut", "Delaware", "Washington DC", "Florida", "Georgia") #saved as results_set_2

system.time(
  for(sex_i in c("Male", "Female")){
    #for(state_i in c("Alabama", "Arizona", "Arkansas", "California")) { #saved as results_set_1
    for(state_i in c("Colorado", "Connecticut", "Delaware", "Washington DC")) { #saved as results_set_2
      assign(paste0("r.White.", gsub(" ", "", state_i), ".", sex_i), run_analysis(dataset = dat.clean, state1 = state_i, sex1 = sex_i, race1 = "White"))
      assign(paste0("r.Black.", gsub(" ", "", state_i), ".", sex_i), run_analysis(dataset = dat.clean, state1 = state_i, sex1 = sex_i, race1 = "Black"))
    }
  }
)

# r.White <- rbind(r.White.AlabamaMale, r.White.ArizonaMale, r.White.ArkansasMale, r.White.CaliforniaMale,
#                  r.White.AlabamaFemale, r.White.ArizonaFemale, r.White.ArkansasFemale, r.White.CaliforniaFemale)
r.White <- rbind(r.White.Colorado.Male, r.White.Connecticut.Male, r.White.Delaware.Male, r.White.WashingtonDC.Male,
                 r.White.Colorado.Female, r.White.Connecticut.Female, r.White.Delaware.Female, r.White.WashingtonDC.Female)
r.White$race <- "White"

# r.Black <- rbind(r.Black.AlabamaMale, r.Black.ArizonaMale, r.Black.ArkansasMale, r.Black.CaliforniaMale,
#                  r.Black.AlabamaFemale, r.Black.ArizonaFemale, r.Black.ArkansasFemale, r.Black.CaliforniaFemale)
r.White <- rbind(r.Black.Colorado.Male, r.Black.Connecticut.Male, r.Black.Delaware.Male, r.Black.WashingtonDC.Male,
                 r.Black.Colorado.Female, r.Black.Connecticut.Female, r.Black.Delaware.Female, r.Black.WashingtonDC.Female)
r.Black$race <- "Black"
```

@@

r.All$smoothed_deaths <- r.All$smoothed_rate*r.All$population
table(r.All$smoothed_deaths == 0) #check this -- if no deaths in an age-band (i.e., no death for any COD, then can't run the COD calculations for that stratum.)

system.time(r.All <- r.All %>% group_by(post.samp, state, race.sex, year.n, age_minbin) %>%
                           arrange(post.samp, state, race.sex, year.n, age_minbin))
```

```{r run_calculations}
#run time: 8.5 hours for four states
#run the life table and decomposition calculations for each of the 1000 posterior samples

@@

```{r save_results}

#SET 1: Alabama, Arizona, Arkansas, California
save(r.All, le.calculations, file = "~/BW_results/results_set_1.Rdata") 
write.csv(x = BlackWhite, file = "~/BW_results/BlackWhite_set_1.csv")
write.csv(x = age.decomp.estimates, file = "~/BW_results/age_decomp_set_1.csv")
write.csv(x = cod.marginal.estimates, file = "~/BW_results/cod_marginal_set_1.csv")
write.csv(x = age.cod.estimates, file = "~/BW_results/age_cod_set_1.csv")
```
